---
title: "RLesson 3 Logistic Regression"
author: "Alan P Zelicoff"
date: "April 4, 2017"
output: html_document
---

```{r, echo=FALSE}

load('rcourse_lesson3_environment.RData')

```

# Introduction

We'll try taking the items that are in the environment from the calculations that have been done and stored in folders:

- the **data** folder has the raw and *cleaned* data
- the **figures** folder has the .pdf documents that display the raw data (in this case as bar plots)
- the **scripts** folder has the code for reading, manipulating, cleaning and organizing the data, creating the figures and of course doing the statistics.

I am going to try to go a bit beyond the exercise in the lesson and try to use the `stargazer` package for presenting the summary of the models.


# Results

## Full Season Data
Here is the win percentage for the San Francisco Giants before and after the World Series break.


```{r, echo=FALSE, fig.align='center'}
allstar.plot
```


## Buster Posey Data

# Conclusion