---
title: "RLesson 3 Logistic Regression"
author: "Alan P Zelicoff"
date: "April 4, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE}

load('rcourse_lesson3_environment.RData')
library(stargazer)
```

# Introduction

We'll try taking the items that are in the environment from the calculations that have been done and stored in folders:

- the **data** folder has the raw and *cleaned* data
- the **figures** folder has the .pdf documents that display the raw data (in this case as bar plots)
- the **scripts** folder has the code for reading, manipulating, cleaning and organizing the data, creating the figures and of course doing the statistics.

I am going to try to go a bit beyond the exercise in the lesson and try to use the `stargazer` package for presenting the summary of the models.


# Results

## Full Season Data
Here is the win percentage for the San Francisco Giants before and after the World Series break.


```{r, echo=FALSE, fig.align='center', fig.height = 3, fig.width = 3}
allstar.plot
```


## Buster Posey Data
But maybe there is something to the belief that when Buster Posey walks the Giants are more likely to win.  Visualization of the data suggests this is the case.  

```{r, echo=FALSE, fig.align='center', fig.height = 3, fig.width = 4.5}
posey_walked.plot
```


## Statistical Model
```{r, echo=FALSE, results = 'asis'}
stargazer::stargazer(allstar.glm, header = FALSE, type = 'latex',
                     title = "Hierarchical (Multi-level) Model Results")
                
```




# Conclusion